Describing demographic models is hard

### 2020-05-20 paper.tex
More analysis of github repos.

This model was subsequently copied
several times and used in publications \jkcomment{do we want to estimate how
many times it was copied? A quick search on github suggests around 30
times]} \dncomment{I like this as a rough metric, like ``the number of copies
is unknown, but we found x copies on github''}

>>>>

This model was subsequently copied
several times and used in publications. By searching for some keywords on
GitHub, we found 33 repositories containing either direct copies of the
erroneous model code, or code that was obviously derived from it.
(We have opened issues on each of these repos to alert the authors.)

\jkcomment{do we want to estimate how
many times it was copied? A quick search on github suggests around 30
times]} \dncomment{I like this as a rough metric, like ``the number of copies
is unknown, but we found x copies on github''}
